\hspace{4em}MOPy is a open source application with GNU - GPL v3 License, with this anyone who is interested in using this application can freely download and use it, and even modify the contents to their requirements. If they wish to contribute to this application they can fork the repository on GitHub[3] and add their contribution by sending a pull request. The reason GNU-GPL v3 license is used is that we aim to keep a quality control to the features that gets added to the application. We are always open to contributors.

There is a list of features with corresponding priorities that are planned to be added down the line. This will be constantly updated indefinitely. And if the user is not able to add a feature then they can request a feature that would be added to the list with a appropriate priority. There is discord server in which anyone can join and hold discussions with other participants. Contributors can hold discussions about the feature they are planning to add, others can discuss about the concepts and request features to be added. 

As of now this runs on Windows only. This could be made to run on other platforms and even as a web application which would negate the need of a moderately powerful hardware. The database could be expanded with much more data than present.

This entire code can be converted into a library that anyone can download from PyPI. This would enable the user to utilize the features directly from the command line or their python projects. This would simplify their projects.